Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-04 hpmoon-asoco.tex
Minor change in reference
More comments on results and images for issue #22

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}. As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be shared in the whole set of different islands. Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified18}.}.
 The whole parameter set is summarized in Table \ref{tab:parameters}.

@@

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt3_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt6_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt6_512}
\end{figure}

%%%%%2018

@@

@@

@@

@@

@@

Problems that require high-performance % problems are not high-performance. They
                          % _require_ high performance Fergu: done
 and deal with a large number of decision variables can leverage the
 division of the decision space that parallel and distributed
 algorithms imply. This can be done in dMOEAs by selective operator application (SLA), that is, dividing the
 chromosome into different parts, each one modified by a different
 island. This paper compares a baseline distributed NSGA-II with three
 different strategies to separate the chromosome (disjoint or
 overlapping parts), using a high number of islands. Results show that
 these methods can achieve better quality metrics than the baseline in
 the same amount of time, with large chromosome lengths.

>>>>

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}. As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be shared in the whole set of different islands. Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified2018}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}.

@@

%ZDT1
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_512}
\end{figure}

@@

%ZDT2
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_512}
\end{figure}

@@

%ZDT3
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt3_512}
\end{figure}

@@

%ZDT6
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt6_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT6 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt6_512}
\end{figure}

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{FINISH THIS SECTION!!!! Plotting the final PFs of each combination of parameters, problems and sizes also allow to see the different .... ZDT1 has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=512$ (Figure \ref{fig:plot_zdt1_2048}) it is visually clear that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}. But if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048}) that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is larger.}

%ZDT2
\textcolor{blue}{ZDT2 has a non-convex Pareto-optimal front. This is the reason that some solutions ....WHAT. As in previous problem, there is a decrease of quality in all configurations when increasing the size of $P$.}

%ZDT3
\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations. However, with $L=512$, some the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to $O$ and $A$). This can be explained because...  In the case of $L=2048$...}

\textcolor{blue}{In ZDT6, the Pareto-optimal solutions are not only non-uniformly distributed along the PF, but their density also increases as we move further away from it. That is the reason why some PFs obtained have a extremely low number of solutions in some configurations, and also, they are aggregated toward the areas with more density...}

@@

Problems that require high-performance 
 and deal with a large number of decision variables can leverage the
 division of the decision space that parallel and distributed
 algorithms imply. This can be done in dMOEAs by selective operator application (SLA), that is, dividing the
 chromosome into different parts, each one modified by a different
 island. This paper compares a baseline distributed NSGA-II with three
 different strategies to separate the chromosome (disjoint or
 overlapping parts), using a high number of islands. Results show that
 these methods can achieve better quality metrics than the baseline in
 the same amount of time, with large chromosome lengths.
